### 2017-02-27 readme.Rmd
update readme
update to readme

p3 <- predict(object=preds,
             model=fm3,
             type = 'response')
plot(p2)
```

@@

\code{eip} (estimate inclusion probabilties)

@@

where $\lambda(u)$ = the intensity value at point $u$ and $A$ is the area of the sampling unit (cell size).
$\lammbda$ is estimated using `density.ppp` from the spatstat package and then converted into a `inclusion.prob` to inform quasi-random background point selection.

>>>>

p3 <- predict(object=preds,
             model=fm3,
             type = 'response')
plot(p3)
```

@@

### Part two - estimating inclusion probabilities to use as a bias layer. (not finished yet)

`eip` is a function which can be used to estimate inclusion probabilities. This layer of probabilities can be used as a bias offset in PPM modelling.

@@

where $\lambda(u)$ = the intensity value at point $u$ and $A$ is the area of the sampling unit (cell size). $\lambda$ is estimated using `density.ppp` from the spatstat package and then converted into a `inclusion.prob` to inform quasi-random background point selection.
